On the combination of Set Functions and Failures

### 2016-08-25 docs/src/external_ops.tex
CASS manual added

external_d_C_prim_sconc :: CP.OP_List CP.C_Char -> CP.OP_List CP.C_Char
                        -> ConstStore -> CP.OP_List CP.C_Char
\end{curry}
First, we import the standard prelude with the name \code{CP}
in order to shorten the writing of type declarations.
In order to write the final code of this operation,
we have to convert the Curry-related types
(like \code{C_Char}) into the corresponding Haskell types (like \code{Char}).
Note that the Curry-related types contain information about
non-deterministic or constrained values
(see \cite{BrasselHanusPeemoellerReck11,BrasselHanusPeemoellerReck11WLP})
that are meaningless in Haskell.
To solve this conversion problem, the implementation of \CYS
provides a family of operations to perform these conversions
for the predefined types occurring in the standard prelude.
For instance, \code{fromCurry} converts a Curry type into the
corresponding Haskell type, and \code{toCurry} converts
the Haskell type into the corresponding Curry type.
Thus, we complete our example with the definition
(note that we simply ignore the final argument representing the
constraint store)
\begin{curry}
external_d_C_prim_sconc s1 s2 _ =
  toCurry ((fromCurry s1 ++ fromCurry s2) :: String)
\end{curry}
Here, we use Haskell's concatenation operation \ccode{++}
to concatenate the string arguments.
The type annotation \ccode{:: String} is necessary
because \ccode{++} is a polymorphic function
so that the type inference system of Haskell
has problems to determine the right instance of the conversion
function.

>>>>

external_d_C_prim_sconc :: CP.OP_List CP.C_Char -> CP.OP_List CP.C_Char
                        -> ConstStore -> CP.OP_List CP.C_Char
\end{curry}
First, we import the standard prelude with the name \code{CP}
in order to shorten the writing of type declarations.
In order to write the final code of this operation,
we have to convert the Curry-related types
(like \code{C_Char}) into the corresponding Haskell types (like \code{Char}).
Note that the Curry-related types contain information about
non-deterministic or constrained values
(see \cite{BrasselHanusPeemoellerReck11,BrasselHanusPeemoellerReck13PADL})
that are meaningless in Haskell.
To solve this conversion problem, the implementation of \CYS
provides a family of operations to perform these conversions
for the predefined types occurring in the standard prelude.
For instance, \code{fromCurry} converts a Curry type into the
corresponding Haskell type, and \code{toCurry} converts
the Haskell type into the corresponding Curry type.
Thus, we complete our example with the definition
(note that we simply ignore the final argument representing the
constraint store)
\begin{curry}
external_d_C_prim_sconc s1 s2 _ =
  toCurry ((fromCurry s1 ++ fromCurry s2) :: String)
\end{curry}
Here, we use Haskell's concatenation operation \ccode{++}
to concatenate the string arguments.
The type annotation \ccode{:: String} is necessary
because \ccode{++} is a polymorphic function
so that the type inference system of Haskell
has problems to determine the right instance of the conversion
function.
